%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy CV/Resume
% XeLaTeX Template
% Version 1.0 (5/5/2014)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Debarghya Das (http://www.debarghyadas.com)
% With extensive modifications by:
% Vel (vel@latextemplates.com)
%
% License:
% CC BY-NC-SA 3.0 (http://creativecommons.org/licenses/by-nc-sa/3.0/)
%
% Important notes:
% This template needs to be compiled with XeLaTeX.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[letterpaper]{deedy-resume} % Use US Letter paper, change to a4paper for A4
\usepackage{nopageno}

\begin{document}

%----------------------------------------------------------------------------------------
%	TITLE SECTION
%----------------------------------------------------------------------------------------

\namesection{Charles P.}{Clermont}{ % Your name
% \urlstyle{same}\url{http://cpclermont.com} \\ % Your website, LinkedIn profile or other web address
github: \href{http://github.com/charlespwd}{charlespwd} \thinspace | linkedin: \href{http://ca.linkedin.com/in/cpclermont}{cpclermont} \thinspace | skype: charles.pclermont \\
\href{mailto:charles@cpclermont.com}{charles@cpclermont.com} \thinspace | +1-514-746-6175 \\[\fpeval{\baseheight}]
}

%
% %------------------------------------------------
% % Summary
% %------------------------------------------------
%
% \section{Summary}
%
% %\subsection{Objective}
% %Passionate about technology, automation and adventure
% %travel, my ambition is to travel
% %the world and do what I do best: solving problems.
%
% %\sectionspace
%
% \subsection{Languages}
% French (fluent), English (fluent)
%
% \sectionspace
% \subsection{Traits}
%   \textbullet{} Resourceful \\
%   \textbullet{} Disciplined \\
%   \textbullet{} Focused \\
%
% \sectionspace
% \subsection{Interests}
%   \textbullet{} Rock-climbing \\
%   \textbullet{} Technology
%
% \sectionspace
% %------------------------------------------------
% % Skills
% %------------------------------------------------
%
% \section{Skills}
%
% \subsection{Programming}
%
% \location{Over 5000 lines:}
% \href{http://github.com/charlespwd/mcgill-minerva-api}{JavaScript}
% \textbullet{}
% \href{http://github.com/charlespwd/bestcase}{Clojure}
% \textbullet{}
% PHP \\
% CSS(SASS)
% \textbullet{}
% \href{http://github.com/charlespwd/tex-base}{\LaTeX}
% \textbullet{}
% \href{http://github.com/charlespwd/suture.m}{MATLAB} \\
% \insectionspace
%
% \location{Over 1000 lines:}
% \href{http://github.com/charlespwd/grocery-list}{Ruby}
% \textbullet{} C \textbullet{} Java
%
% \insectionspace
%
% \location{Familiar:}
% Python \textbullet{} MySQL \textbullet{} MongoDB
%
% \sectionspace % Some whitespace after the section
%
% \subsection{Frameworks}
%
% \location{JavaScript}
% NodeJS \textbullet{} AngularJS \textbullet{} EmberJS \\
% jQuery \textbullet{} D3js \textbullet{} ES6 \\
%
% \insectionspace
% %
% % \location{Others}
% % PHP: YII \textbullet{} CSS: SASS/LESS \textbullet{} \\
% % Ruby: Rails
% %
% \sectionspace
%
%----------------------------------------------------------------------------------------

%------------------------------------------------
% Summary
%------------------------------------------------

\section{Summary}
\flushleft\location{} % fix font size to match

Independent front-end developer with a degree in engineering. Self-taught
in the ways of computers since 2003. My specialties are JavaScript,
ember, backbone, node.js, D3, Clojure and ClojureScript. I make web apps.


\sectionspace % Some whitespace after the section

%------------------------------------------------
% Education
%------------------------------------------------

\section{Education}

\runsubsection{Bachelor of Engineering}\descript{| \thinspace McGill University} \\
% \descript{Honours Mechanical Engineering}
\location{Honours Mechanical Engineering \thinspace | \thinspace Class of 2015}

\begin{tightitemize}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\item Honours Thesis - \href{https://dl.dropboxusercontent.com/u/14503566/thesis.pdf}{\textit{Efficient Optimization of Expensive Black-box Functions}}

\item Honours Design Project - \href{https://dl.dropboxusercontent.com/u/14503566/thesis.pdf}{\textit{Optimal
Design of Glass}}
\end{tightitemize}

\insectionspace
\location{Relevant Advanced Courses}
\begin{tightitemize}
% \vspace{\topsep} % Hacky fix for awkward extra vertical space
\item Computational Aerodynamics
\item Mathematical Programming
\item Theory of Computation

\end{tightitemize}
\insectionspace

Groups: HackMcGill, McGill Outdoors Club. CGPA: 3.6

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Experience
%------------------------------------------------

\section{Experience}

%------------------------------------------------
\runsubsection{Front-end Developer}
\descript{| \thinspace Independent}

\location{May 2014 – Present \thinspace | \thinspace Montreal, QC}

\\[\fpeval{\baseheight}]

Role(s):

\begin{tightitemize}
    \item Lead a team of freelancers for the front-end of Keylocation.sg;
    \item Perform code review, and offer recommendations to clients;
    \item Contribute to and maintain Open Source Software;
    \item Write tested, efficient and maintainable software;
\end{tightitemize}

\\[\fpeval{\baseheight}]

Product(s):
\begin{tightitemize}
    \item The front-end of Keylocation.sg; an EmberJS application;
    \item An in-browser recorded-audio to visualisation library;
    \item Contributions to Open Source Software\textemdash Bestcase, Request, peaks.js;
    \item Open Source libraries\textemdash myMinerva, McGill-Minerva-API;
    \item My-McGill.ca\textemdash a service that sends an email notification when new grades come in.;
    \item Store Statistics\textemdash a Shopify app;
    \item Time Travel Pong\textemdash a game.
\end{tightitemize}

\\[\fpeval{\baseheight}]

Technologies: \\
\begin{tightitemize}
    \item Keylocation\textemdash EmberJS, node.js, jade, LESS, PostgreSQL, grunt, vagrant, git;
    \item Audio Library\textemdash ES6, browserify, grunt, bower, UMD, AngularJS(as example use), git;
    \item Request, peaks.js, McGill-Minerva-API\textemdash plain ol' javascript, node.js, grunt, git;
    \item Bestcase, myMinerva, my-mcgill.ca\textemdash Clojure, ClojureScript, MongoDB, HTML5, git;
    \item Store Statistics\textemdash Clojure, ES6, HTML5, SASS, core.async, D3, grunt, git;
    \item Time Travel Pong\textemdash ClojureScript, git;
\end{tightitemize}


\sectionspace % Some whitespace after the section
%----------------------------------------------------------------------------------------
%	SECOND PAGE (EXAMPLE)
%----------------------------------------------------------------------------------------

\newpage % Start a new page

%\begin{minipage}[t]{0.33\textwidth} % The left column takes up 33% of the text width of the page
\namesection{Charles P.}{Clermont}{}

\section{EXPERIENCE~\small{Cont'd}}

\runsubsection{Bombardier Aerospace}
\descript{| \thinspace Intern Developer}

\location{June 2010 – Jan 2014 \thinspace | \thinspace Montreal, QC}
\\[\fpeval{\baseheight}]

Role(s):

\begin{tightitemize}
    \item Develop and translate technical documentation for SAP;
\end{tightitemize}

\\[\fpeval{\baseheight}]

Product(s):
\begin{tightitemize}
    \item A student time sheet portal which saves HR 1200 hours every year.
    \item A VBA macro which saved 200 hours of manual Excel to MySQL database migration;
    \item Various team-wide work-flow improvements;
    \item Technical Documentation.
\end{tightitemize}

\\[\fpeval{\baseheight}]

Technologies: \\
\begin{tightitemize}
    \item Time Sheet Portal\textemdash PHP, YII, MySQL, HTML, jQuery, CSS, git;
    \item Database Migration, work-flow improvements\textemdash Excel and PowerPoint VBA;
    \item Technical Documentation\textemdash SAP, Camtasia Studio, Assima.
\end{tightitemize}

\sectionspace % Some whitespace after the section

%------------------------------------------------
% Research
%------------------------------------------------

\section{Projects}

\runsubsection{Store Statistics for Shopify}
\descript{| \thinspace \href{http://apps.shopify.com/store-statistics}{apps.shopify.com/store-statistics}}

\location{April 2015 – Present \thinspace | \thinspace Montreal, QC}
A Software as a Service enabling store owners to have their store's most important
statistics in one click without wasting hours in Excel.
\sectionspace

\runsubsection{bestcase}
\descript{| \thinspace \href{http://github.com/charlespwd/bestcase}{github.com/charlespwd/bestcase}}

\location{February 2015 – Present \thinspace | \thinspace Montreal, QC}
An A/B testing library.
\sectionspace

\runsubsection{Time Travel Pong}
\descript{| \thinspace \href{http://charlespwd.github.io/time-travel-pong}{charlespwd.github.io/time-travel-pong}}

\location{March 2015 \thinspace | \thinspace Montreal, QC}
The game Pong with a twist: you can go back in time.
\sectionspace

\runsubsection{My-McGill Email Service}
\descript{| \thinspace \href{http://my-mcgill.ca}{my-mcgill.ca}}

\location{December 2014 \thinspace | \thinspace Montreal, QC}
A service that sends an email notification to students when new grades
come in.
\sectionspace

\runsubsection{McGill Minerva API}
\descript{| \thinspace \href{https://www.npmjs.org/package/mcgill-minerva-api}{npmjs.org/package/mcgill-minerva-api}}

\location{June 2014 \thinspace | \thinspace Montreal, QC}
A JavaScript abstraction of McGill's registration system.

\sectionspace

\runsubsection{South East Asia}
\descript{| \thinspace Solo Backpacker}

\location{January 2014 – May 2014 \thinspace | \thinspace Singapore, Malaysia, Thailand, Laos, Nepal}
The Annapurna circuit trek, rock-climbing in Krabi and Thakhek,
motorbike travel, bungee jumping, canyon swing, yoga and lots
of books.

\sectionspace % Some whitespace after the section

\\[\fpeval{\baseheight * \golden ^ 4}]
% \center
\textit{Outside of work, I read and climb rocks.}
% %------------------------------------------------
% % Awards
% %------------------------------------------------
%
% \section{Award}
%
% \begin{tabular}{rl}
% 2010-2014	 & JTI MacDonald Corp. Scholarship\\
% \end{tabular}
%
% \sectionspace % Some whitespace after the section
%

%----------------------------------------------------------------------------------------

\end{document}
